\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage{parskip}

\pagestyle{empty}
\hyphenpenalty=10000
\exhyphenpenalty=10000

\begin{document}

\begin{center}
{\Large\bfseries Cover Letter}\\[0.4em]
{\bfseries Manuscript TCOM-TPS-26-0080}\\[0.3em]
Joint Laser Inter-Satellite Link Matching and Traffic Flow Routing in LEO Mega-Constellations via Lagrangian Duality\\[0.3em]
Zhouyou Gu, Jinho Choi, and Jihong Park
\end{center}

\vspace{1em}

\noindent Dear Editor(s),

We are pleased to resubmit our manuscript entitled ``Joint Laser Inter-Satellite Link Matching and Traffic Flow Routing in LEO Mega-Constellations via Lagrangian Duality'' to IEEE Transactions on Communications. The manuscript was previously received with three reviewer reports. After careful examination, the comments from Reviewer 2 appeared unrelated to the submitted work. In contrast, the comments from Reviewers 1 and 3 were relevant and constructive. Following guidance from the IEEE Transactions on Communications editorial team, we are therefore resubmitting the revised manuscript as a new submission representing a major revision of the original work.

The revised manuscript has been substantially strengthened. At a high level, we added a clearer step-by-step NP-hardness proof and clarified the theoretical contribution and its scope, made the modeling assumptions more explicit and practically grounded, expanded the evaluation with stronger comparisons and more realistic constellation settings, and improved the presentation of the main results. We also clarified the intended system-operation setting, refined the traffic and capacity explanations, and performed a focused writing and typo cleanup.

A detailed point-by-point response letter is submitted together with the revised manuscript. The response letter addresses all comments from Reviewers 1 and 3.

Thank you for considering our revised manuscript for publication in IEEE Transactions on Communications.

\vspace{1em}

\noindent Sincerely,\\
Zhouyou Gu, Jinho Choi, and Jihong Park

\end{document}
